---
title: "Analysis of the ChickWeight dataset"
subtitle: 'MSc in Statistics 2026/27, Imperial College London, Data Science Workshop 1c'
author: "Sai Han Myo Htet"
format:
  html:
    toc: true
    highlight: tango
    self-contained: true
    df-print: paged
  pdf: default
format-links: false
bibliography: "chickWeight.bib" 
---

```{=html}
<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>
```

```{r setup, include = FALSE, tidy=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
include_solutions <- TRUE
```

```{r setup2, include=FALSE, tidy=TRUE}
library(rmarkdown)
library(knitr)
library(kableExtra)
library(magrittr)
# Put any library imports and other preamble here.
```

## Introduction

```{r echo = FALSE}

chicks <- ChickWeight
```

In this report, we perform a rudimentary analysis of the built-in ChickWeight Dataset in R. 

```{r echo = FALSE}
#| label: tbl-chicks
#| tbl-cap: "Example rows of the ChickWeight Dataset."
kable(head(chicks))
```

@tbl-chicks give example data entries from the ChickWeight dataset.


# Code appendix

Rather than re-paste all the code to the appendix, here is a trick which makes the markdown file output all the code (without) execution in the appendix, without any duplication.

Please keep in mind to format the code so that the entire code is clearly visible and does not run into the margins of the pdf version.

```{r ref.label=knitr::all_labels(), echo = T, eval = F}
```

# References
